Contextual Combinatorial Cascading Bandits

### 2015-12-04 contextual combinatorial cascading bandits.tex

The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $\theta_*^{\top}x_{t,a}$ is proved in the following lemma.
\begin{lemma}
\label{lem:estimateU}
When (\ref{eq:estimateTheta}) holds for time $t$, we have
$$
0 \leq \bU_t(a) - \theta_{\ast}^{\top}x_{t,a} \leq 2\beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}
\begin{proof}
\begin{align*}
\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
&\leq \beta_{t}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
\end{align*}
\end{proof}

Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}. First, it computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$. Second, it recommends an action $\bA_t$ by the offline oracle with estimated weights $\bU_t$. Third, play $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where 
$$
\bw_t(\ba_{k}^t) = \begin{cases} 0, ~~k < \bO_t\\ 1, ~~k = \bO_t\end{cases}
$$ 
or
$$
\bw_t(\ba_k^t) = 1, k \leq \bO_t = \abs{\bA_t}.
$$
Then, the learning agent update $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\beta_t(\delta)$. In this part, we use the notation $[A; B]$ to denote a matrix $\begin{pmatrix} A\\ B\end{pmatrix}$.

\begin{algorithm}
\caption{ConComCascade}
\label{alg:ConComCascade}
\begin{algorithmic}[1]
\STATE {//Initialization}
\STATE {Parameters: $\delta > 0, \lambda \geq C_\gamma$}
\STATE {Parameters: $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$}
\STATE {$\hat{\theta}_0 = 0, \beta_0(\delta) = 1, \bV_0 = \lambda I$}
\STATE{}

\FORALL {$t=1,2,\ldots$}
\STATE {Obtain context $x_{t,a}$ for all $a\in E$}
\STATE{}

\STATE {//Compute UCBs}
\STATE {$\forall a\in E: $}
\STATE {$\bU_t(a) \leftarrow \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
\STATE {}

\STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
\STATE {$\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \argmax_{A \in \cS} f(A, \bU_t)$}
\STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
\STATE {}

>>>>

The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $\theta_*^{\top}x_{t,a}$ is proved in the following lemma.
\begin{lemma}
\label{lem:estimateU}
When Eq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
$$
0 \leq \bU_t(a) - \theta_{\ast}^{\top}x_{t,a} \leq 2\beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}
\begin{proof}
\begin{align*}
\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
&\leq \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
\end{align*}
\end{proof}

Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}. First, it computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$. Second, it recommends an action $\bA_t$ by the offline oracle with estimated weights $\bU_t$. Third, play $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where 
$$
\bw_t(\ba_{k}^t) = \begin{cases} 0, ~~k < \bO_t\\ 1, ~~k = \bO_t\end{cases}
$$ 
or
$$
\bw_t(\ba_k^t) = 1, k \leq \bO_t = \abs{\bA_t}.
$$
Then, the learning agent update $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\beta_t(\delta)$. In this part, we use the notation $[A; B]$ to denote the matrix obtained by stack A and B vertically like
 $\begin{pmatrix} A\\ B\end{pmatrix}$.

\begin{algorithm}
\caption{ConComCascade}
\label{alg:ConComCascade}
\begin{algorithmic}[1]
\STATE {//Initialization}
\STATE {Parameters: $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$}
\STATE {Parameters: $\delta > 0, \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
\STATE {$\hat{\theta}_0 = 0, \beta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
%\STATE{}

\FORALL {$t=1,2,\ldots$}
\STATE {Obtain context $x_{t,a}$ for all $a\in E$}
%\STATE{}

\STATE {//Compute UCBs}
\STATE {$\forall a\in E: $}
\STATE {$\bU_t(a) \leftarrow \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
%\STATE {}

\STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
\STATE {$\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \argmax_{A \in \cS} f(A, \bU_t)$}
\STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
%\STATE {}
